Real-time resolution of short-read assembly graph using ONT long reads

### 2020-08-09 plos_latex_edit.tex
lrscaf included

% Results and Discussion can be combined.
\section*{Results}
\subsection*{Evaluation using synthetic data}
To evaluate the performance of the method, \npgraph{} 1.1 was tested along with \spades{}, \spades{} hybrid from version 3.13.1, ~\cite{AntipovKM2015}, \npscarf{} (japsa 1.7-02), and \unicycler{} version 0.4.6 %%COMMENT_LC - why just indicate unicyler version and not others? 
using \unicycler{}`s synthetic data set~ \cite{Wick2017unicycler} . 
The data set is a simulation of Illumina and MinION raw data, generated \emph{in silico} based on available microbial references.
We ran hybrid assembly methods using the entire nanopore data and the reciprocal results were evaluated by QUAST 5.0.2~\cite{Mikheenko2018quast5}.

@@

\begin{figure}[!ht]
 \includegraphics[width=\textwidth]{images/FigS2.eps}
 \caption{Alignments of an \emph{Enterobacter~cloacae} reference genome to assembly sequences generated by  (a)~\unicycler{} and (b)~\npgraph{}. The former suggests a structural variant, the latter is virtually an 1-to-1 mapping.}
\end{figure}

\clearpage
\paragraph*{S1 Table.}
\label{S1_Table}
Benchmarking \npgraph{} against \npscarf{} versions, $\mathtt{hybridSPAdes}$ and \unicycler{} hybrid assembler with the synthetic data set.

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

\end{thebibliography}

>>>>

% Results and Discussion can be combined.
\section*{Results}
\subsection*{Evaluation using synthetic data}
To evaluate the performance of the method, \npgraph{} 1.1 was tested along with \spades{}, \spades{} hybrid from version 3.13.1, ~\cite{AntipovKM2015}, \npscarf{} (japsa 1.7-02), and \unicycler{} version 0.4.6 using \unicycler{}`s synthetic data set~ \cite{Wick2017unicycler} . 
\replace{}
The data set is a simulation of Illumina and MinION raw data, generated \emph{in silico} based on available microbial references.
We ran hybrid assembly methods using the entire nanopore data and the reciprocal results were evaluated by QUAST 5.0.2~\cite{Mikheenko2018quast5}.

@@

\begin{figure}[!ht]
 \includegraphics[width=\textwidth]{images/FigS2.eps}
 \caption{Alignments of an \emph{Enterobacter~cloacae} reference genome to assembly sequences generated by  (a)~\cancel{\unicycler{}}\replace{\npgraph{}} and (b)~\cancel{\npgraph{}}\replace{\unicycler{}}. The former suggests a structural variant, the latter is virtually an 1-to-1 mapping.}
\end{figure}

\clearpage
\paragraph*{S1 Table.}
\label{S1_Table}
Benchmarking different methods using $\mathtt{\replace{lrscaf}}$, \npscarf{}, \npgraph{}, $\mathtt{hybridSPAdes}$ and \unicycler{} hybrid assembler with the synthetic data set.

@@

& \replace{lrscaf} & \replace{-} & \replace{-} & \replace{-} & \replace{-} & \replace{-} & \replace{-} \\*

@@

& \replace{lrscaf} & \replace{4113104} & \replace{6} & \replace{4002298} & \replace{0} & \replace{0.00} & \replace{0.00}\\*

@@

& \replace{lrscaf} & \replace{4119020} & \replace{12} & \replace{4002117} & \replace{0} & \replace{0.03} & \replace{0.79}\\* 

@@

& \replace{lrscaf} & \replace{3896799} & \replace{4} & \replace{3886381} & \replace{0} & \replace{0.47} & \replace{
0.36}\\*

@@

& \replace{lrscaf} & \replace{4367657} & \replace{27} & \replace{1035967} & \replace{13} & \replace{30.11} & \replace{1.42}\\* 

@@

& \replace{lrscaf} & \replace{4732001} & \replace{16} & \replace{692794} & \replace{7} & \replace{3.42} & \replace{0.58}\\*

@@

& \replace{lrscaf} & \replace{5410854} & \replace{21} & \replace{910949} & \replace{9} & \replace{13.70} & \replace{0.87}\\*

@@

& \replace{lrscaf} & \replace{5512518} & \replace{20} & \replace{777919} & \replace{26} & \replace{3.52} & \replace{0.38}\\*

@@

& \replace{lrscaf} & \replace{5823340} & \replace{38} & \replace{559414} & \replace{7} & \replace{5.92} & \replace{1.27}\\*

@@

& \replace{lrscaf} & \replace{5470282} & \replace{8} & \replace{2951488} & \replace{9} & \replace{3.04} & \replace{2.62}\\*

@@

& \replace{lrscaf} & \replace{4260869} & \replace{12} & \replace{3215170} & \replace{8} & \replace{6.69} & \replace{2.27}\\*

@@

& \replace{lrscaf} & \replace{12486884} & \replace{214} & \replace{254587} & \replace{27} & \replace{16.45} & \replace{1.97}\\*

@@

& \replace{lrscaf} & \replace{4678609} & \replace{175} & \replace{376897} & \replace{26} & \replace{3.91} & \replace{2.35}\\*

@@

& \replace{lrscaf} & \replace{5266645} & \replace{128} & \replace{429353} & \replace{27} & \replace{9.72} & \replace{1.19}\\*

@@

& \replace{lrscaf} & \replace{2231488} & \replace{10} & \replace{683404} & \replace{6} & \replace{11.96} & \replace{1.37}\\*

@@

\bibitem{Qin2019}
Qin, M., Wu, S., Li, A., Zhao, F., Feng, H., Ding, L., Ruan, J
\newblock {{LRScaf}: improving draft genomes using long noisy reads}
\newblock BMC Genomics. 2019;20(1):955
\end{thebibliography}
